---
title: "Terrorism in Europe"
author: "Hugo Day"
date: "15 August 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
library(dplyr)
dataRaw<-read.csv2("./eu_terrorism_fatalities_by_country.csv",header = TRUE,sep=",") 
```

```

## Deaths by Terrorism: An example analysis

This is a presentation for you dear presenter, to take part in exploring the wonderful power of Plot.ly and R markdown. To illustrate this we're going to use the terrorism data provided by FiveThirtyEight. Go to the next side to witness the true power of the this tool set.

## Plots most Erksome

```{r, echo=FALSE, warning=FALSE}
f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#7f7f7f"
)
x <- list(
  title = "Year",
  titlefont = f
)
y <- list(
  title = "Deaths by Terrorism",
  titlefont = f
)

p<-plot_ly(data=dataRaw,x=~iyear, y=~Belgium,name="Belgium",type="scatter",mode="lines") %>%
  add_trace(x=~iyear,y=~Denmark,name="Denmark") %>%
  add_trace(x=~iyear,y=~France,name="France") %>%
  add_trace(x=~iyear,y=~Germany,name="Germany") %>%
  add_trace(x=~iyear,y=~Greece,name="Greece") %>%
  add_trace(x=~iyear,y=~Ireland,name="Ireland") %>%
  add_trace(x=~iyear,y=~Italy,name="Italy") %>%
  add_trace(x=~iyear,y=~Luxembourg,name="Luxembourg") %>%
  add_trace(x=~iyear,y=~Netherlands,name="Netherlands") %>%
  add_trace(x=~iyear,y=~Portugal,name="Portugal") %>%
  add_trace(x=~iyear,y=~Spain,name="Spain") %>%
  add_trace(x=~iyear,y=~United.Kingdom,name="United Kingdom") %>%
  layout(xaxis=x,yaxis=y)
p
```